Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2022-03-14 OSF Files/Data Analysis/Supplemental-Material-B-Annotated-Analysis.Rmd
osf files added

(
  mdlWorkerOut$Att$predPltSlopesCore <-
    ggplot(data = mdlWorkerOut$Att$predSlopesCore, aes(x = session, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
    facet_wrap( ~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCore.png",
  mdlWorkerOut$Att$predPltSlopesCore,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)
```

@@

# Save variances
mdlWorkerOut$Qlt$varSlopesCore <- 
  lme4::VarCorr(mdlWorkerOut$Qlt$lmeSlopesCore)
```

@@

(
  mdlStudentOut$Att$predPltSlopesCore <-
    ggplot(data = mdlStudentOut$Att$predSlopesCore %>% filter(PID %in% studentOutPltIDs), 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap( ~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCore.png",
  mdlStudentOut$Att$predPltSlopesCore,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)
```

@@

(
  mdlStudentOut$Qlt$predPltSlopesCore <-
    ggplot(data = mdlStudentOut$Qlt$predSlopesCore %>% filter(PID %in% studentOutPltIDs), 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap(~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/StudentOut_PredictionPlot_SlopesCore.png",
  mdlStudentOut$Qlt$predPltSlopesCore,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)
```

@@

(
  mdlMedicalOut$Att$predPltSlopesAllport <-
    ggplot(data = mdlMedicalOut$Att$predSlopesAllport, 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap( ~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttAllport.png",
  mdlMedicalOut$Att$predPltSlopesAllport,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)
```

@@

@@

(
  mdlMedicalOut$Att$predPltSlopesCore <-
    ggplot(data = mdlMedicalOut$Att$predSlopesCore, 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap( ~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCore.png",
  mdlMedicalOut$Att$predPltSlopesCore,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)
```

@@

(
  mdlMedicalOut$Qlt$predPltSlopesCore <-
    ggplot(data = mdlMedicalOut$Qlt$predSlopesCore %>% filter(PID %in% medicalOutPltIDs), 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap(~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/MedicalOut_PredictionPlot_SlopesCore.png",
  mdlMedicalOut$Qlt$predPltSlopesCore,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)
```

@@

![ore Need Fulfillment predicting Outgroup Attitudes.](Figures/forestParametricFETheoryAttitudeCore.png)

>>>>

(
  mdlWorkerOut$Att$predPltSlopesCore <-
    ggplot(data = mdlWorkerOut$Att$predSlopesCore, aes(x = session, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
    facet_wrap( ~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCore.png",
  mdlWorkerOut$Att$predPltSlopesCore,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)

ggplot(data = workerOutWithinBetween,
       aes(y = thermometerDutch_1, x = keymotive_fulfillemt_1, col = as.factor(PID))) +
  geom_point(size = 1) + # change size and colour
  labs(y = "Outgroup Attitudes", 
       x = "Key Need Fulfillment",
       ) + # rename axes
  scale_y_continuous(limits = c(0, 100),
                     breaks = c(0, 20, 40, 60, 80, 100)) + # y axis limits/range (0, 100), break points
  #scale_x_continuous(limits = c(90, 130)) + # x axis limits/range
  #geom_smooth(method = 'lm', se = F, aes(group = as.factor(PID))) + # fit linear regression line
  geom_smooth(method = 'lm', se = F, aes(group = 1), col = "red", linetype = "longdash") +
  geom_line(stat="smooth", 
            method = "lm", 
            formula = y ~ x,
            size = 1,
            alpha = 0.5) +
  theme_Publication() +
  theme(legend.position = "none")

@@

# Save variances
mdlWorkerOut$Qlt$varSlopesCore <- 
  lme4::VarCorr(mdlWorkerOut$Qlt$lmeSlopesCore)

ggplot(data = workerOutWithinBetween,
       aes(y = quality_overall_1, x = keymotive_fulfillemt_1, col = as.factor(PID))) +
  geom_point(size = 1) + # change size and colour
  labs(y = "Interaction Quality", 
       x = "Key Need Fulfillment",
       ) + # rename axes
  scale_y_continuous(limits = c(-50, 50)) + # y axis limits/range (0, 100), break points
  #scale_x_continuous(limits = c(90, 130)) + # x axis limits/range
  #geom_smooth(method = 'lm', se = F, aes(group = as.factor(PID))) + # fit linear regression line
  geom_smooth(method = 'lm', se = F, aes(group = 1), col = "red", linetype = "longdash") +
  geom_line(stat="smooth", 
            method = "lm", 
            formula = y ~ x,
            size = 1,
            alpha = 0.5) +
  theme_Publication() +
  theme(legend.position = "none")
```

@@

(
  mdlStudentOut$Att$predPltSlopesCore <-
    ggplot(data = mdlStudentOut$Att$predSlopesCore %>% filter(PID %in% studentOutPltIDs), 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap( ~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCore.png",
  mdlStudentOut$Att$predPltSlopesCore,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)

ggplot(data = studentOutWithinBetween,
       aes(y = AttitudesDutch, x = KeyNeedFullfillment, group = as.factor(PID))) +
  geom_point(size = 1, alpha = .2, position = position_jitter(width = 3, height = 3)) + # change size and colour
  labs(y = "Outgroup Attitudes", 
       x = "Key Need Fulfillment",
       ) + # rename axes
  scale_y_continuous(limits = c(0, 100)) + # y axis limits/range (0, 100), break points
  #scale_x_continuous(limits = c(90, 130)) + # x axis limits/range
  #geom_smooth(method = 'lm', se = F, aes(group = as.factor(PID))) + # fit linear regression line
  geom_line(stat="smooth", 
            method = "lm", 
            formula = y ~ x,
            size = 1,
            alpha = 0.33) +
  geom_smooth(method = 'lm', se = F, aes(group = 1), col = "red") +
  theme_Publication() +
  theme(legend.position = "none")
```

@@

(
  mdlStudentOut$Qlt$predPltSlopesCore <-
    ggplot(data = mdlStudentOut$Qlt$predSlopesCore %>% filter(PID %in% studentOutPltIDs), 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap(~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/StudentOut_PredictionPlot_SlopesCore.png",
  mdlStudentOut$Qlt$predPltSlopesCore,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)

ggplot(data = studentOutWithinBetween,
       aes(y = quality_overall, x = KeyNeedFullfillment, group = as.factor(PID))) +
  geom_point(size = 1, alpha = .2, position = position_jitter(width = 3, height = 3)) + # change size and colour
  labs(y = "Interaction Quality", 
       x = "Key Need Fulfillment",
       ) + # rename axes
  scale_y_continuous(limits = c(0, 100)) + # y axis limits/range (0, 100), break points
  #scale_x_continuous(limits = c(90, 130)) + # x axis limits/range
  #geom_smooth(method = 'lm', se = F, aes(group = as.factor(PID))) + # fit linear regression line
  geom_line(stat="smooth", 
            method = "lm", 
            formula = y ~ x,
            size = 1,
            alpha = 0.33) +
  geom_smooth(method = 'lm', se = F, aes(group = 1), col = "red") +
  theme_Publication() +
  theme(legend.position = "none")
```

@@

(
  mdlMedicalOut$Att$predPltSlopesAllport <-
    ggplot(data = mdlMedicalOut$Att$predSlopesAllport, 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap( ~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttAllport.png",
  mdlMedicalOut$Att$predPltSlopesAllport,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)

ggplot(data = medicalOutWithinBetween,
       aes(y = AttitudesDutch, x = AllportsCondition, group = as.factor(PID))) +
  geom_point(size = 1, alpha = .15, position = position_jitter(width = 3, height = 3)) + # change size and colour
  labs(y = "Outgroup Attitude", 
       x = "Fulfillment Allport's Conditions",
       ) + # rename axes
  scale_y_continuous(limits = c(0, 100)) + # y axis limits/range (0, 100), break points
  #scale_x_continuous(limits = c(90, 130)) + # x axis limits/range
  #geom_smooth(method = 'lm', se = F, aes(group = as.factor(PID))) + # fit linear regression line
  geom_line(stat="smooth", 
            method = "lm", 
            formula = y ~ x,
            size = 1,
            alpha = 0.33) +
  geom_smooth(method = 'lm', se = F, aes(group = 1), col = "red") +
  theme_Publication() +
  theme(legend.position = "none")
```

@@

ggplot(data = medicalOutWithinBetween,
       aes(y = qualityOverall, x = AllportsCondition, group = as.factor(PID))) +
  geom_point(size = 1, alpha = .15, position = position_jitter(width = 3, height = 3)) + # change size and colour
  labs(y = "Interaction Quality", 
       x = "Fulfillment Allport's Conditions",
       ) + # rename axes
  scale_y_continuous(limits = c(0, 100)) + # y axis limits/range (0, 100), break points
  #scale_x_continuous(limits = c(90, 130)) + # x axis limits/range
  #geom_smooth(method = 'lm', se = F, aes(group = as.factor(PID))) + # fit linear regression line
  geom_line(stat="smooth", 
            method = "lm", 
            formula = y ~ x,
            size = 1,
            alpha = 0.33) +
  geom_smooth(method = 'lm', se = F, aes(group = 1), col = "red") +
  theme_Publication() +
  theme(legend.position = "none")
```

@@

(
  mdlMedicalOut$Att$predPltSlopesCore <-
    ggplot(data = mdlMedicalOut$Att$predSlopesCore, 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap( ~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCore.png",
  mdlMedicalOut$Att$predPltSlopesCore,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)

ggplot(data = medicalOutWithinBetween,
       aes(y = AttitudesDutch, x = KeyNeedFulfillment, group = as.factor(PID))) +
  geom_point(size = 1, alpha = .15, position = position_jitter(width = 3, height = 3)) + # change size and colour
  labs(y = "Outgroup Attitudes", 
       x = "Keyneed Fulfillment",
       ) + # rename axes
  scale_y_continuous(limits = c(0, 100)) + # y axis limits/range (0, 100), break points
  #scale_x_continuous(limits = c(90, 130)) + # x axis limits/range
  #geom_smooth(method = 'lm', se = F, aes(group = as.factor(PID))) + # fit linear regression line
  geom_line(stat="smooth", 
            method = "lm", 
            formula = y ~ x,
            size = 1,
            alpha = 0.33) +
  geom_smooth(method = 'lm', se = F, aes(group = 1), col = "red") +
  theme_Publication() +
  theme(legend.position = "none")
```

@@

(
  mdlMedicalOut$Qlt$predPltSlopesCore <-
    ggplot(data = mdlMedicalOut$Qlt$predSlopesCore %>% filter(PID %in% medicalOutPltIDs), 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap(~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/MedicalOut_PredictionPlot_SlopesCore.png",
  mdlMedicalOut$Qlt$predPltSlopesCore,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)

ggplot(data = medicalOutWithinBetween,
       aes(y = qualityOverall, x = KeyNeedFulfillment, group = as.factor(PID))) +
  geom_point(size = 1, alpha = .15, position = position_jitter(width = 3, height = 3)) + # change size and colour
  labs(y = "Interaction Quality", 
       x = "Keyneed Fulfillment",
       ) + # rename axes
  scale_y_continuous(limits = c(0, 100)) + # y axis limits/range (0, 100), break points
  #scale_x_continuous(limits = c(90, 130)) + # x axis limits/range
  #geom_smooth(method = 'lm', se = F, aes(group = as.factor(PID))) + # fit linear regression line
  geom_line(stat="smooth", 
            method = "lm", 
            formula = y ~ x,
            size = 1,
            alpha = 0.33) +
  geom_smooth(method = 'lm', se = F, aes(group = 1), col = "red") +
  theme_Publication() +
  theme(legend.position = "none")
```

@@

![Core Need Fulfillment predicting Outgroup Attitudes.](Figures/forestParametricFETheoryAttitudeCore.png)
